\documentclass[12pt]{article}
\title{WRITEUP ON FUTURE OF HEALTHCARE}
\author{Bhumika Dewangan}
\date{}
\begin{document}
\maketitle
\section{INTRODUCTION}
The ferocity of pandemic has proved that how crucial is the availability of virtual healthcare services along with guaranteed quality for strengthening the humanity and for survival.Telemedicine is the gamechanger for sure in upcoming years.Industry players are watching with interest as AI/ML-reliant healthcare applications emerge.
\section{TECHNOLOGICAL ADVANCEMENTS}
\begin{itemize}
\item

PATIENTS EDUCATION-Patient First is a program to Develop healthcare IT Solutions for educating patients about healthcare. Patient First aims to educate patients and make their user-experience easy through responsive innovations in health and technology. Patients can learn about potential health concerns, the risk factors, and what they can do to deal with such issues. It includes all the latest healthcare technologies, such as patient engagement, mHealth solutions, and UI/UX platforms that are user friendly.\\
\item
REMOTE PATIENT MONITORING-The association of technology and healthcare has seen a rise in virtual healthcare, which means more online appointments, real-time televisits, and remote care. Physicians would need to monitor vitals and keep track of health conditions of the patients. This can be achieved easily by remote patient monitoring (RPM). RPM tools include internet-based devices such as health bands, blood pressure cuffs, blood-oxygen sensors, IoT glucose meters, and IoT thermometers. Real-time data can be collected through these devices, which the physicians can receive and interpret online.  
\item
TELEMEDICINE-It is the delivery of healthcare services, where distance is a critical factor, by all healthcare professionals using information and communication technologies for the exchange of valid information for diagnosis, treatment and prevention of disease and injuries, research and evaluation and for the continuing education of healthcare providers, all in the interests of advancing the health of individuals and their communities.This has revolutionised the future of healthcare sector.
\item
BLOCKCHAIN-With its decentralised nature the flexibility in securing the data and medical records of individual it provides is not comparable.The technology is already being used to do everything from securely encrypt patient data to manage the outbreak of harmful diseases. It is shareable with only the parties authorized for access at the moments when they need it.
\item
AUGMENTED REALITY-It is the technology that allows laying some information, videos, and graphics on smart devices over reality. with AR maps layered over reality people can find medical centers, pharmacies, and other healthcare facilities.This can be used to study different parts of body more effectively.
\item
VIRTUAL REALITY- It is a simulated reality created by computer technology when a person completely immerses into a digital environment. robotic devices perform high precision operations controlled by a human surgeon with VR technology, VR helps patients to easier overcome high pain levels and ensure faster recovery when performing physical therapy, patients can use VR for meditations or relaxation in safe environments provided by VR.

\end{itemize}
\section{CONCLUSION}
This modern era is transforming towards a lot more innovations in the field of technology ,artificial intelligence,and machine learning and hence removing barrier of all sorts.
\end{document}